Tidy data structure to support exploration and modeling of temporal-context data

### 2018-08-20 main.Rmd
added a bit on tidy data

@wickham2014tidy coined the term "tidy data", which is a rephrasing of the second and third normal forms in relational databases. and formalized the processing from messy data to "tidy data". These principles attempt to standardize the mapping from the semantics of a dataset to its structure and facilitate data analysis in a coherent way. Based on the systematic structuring principles, the grammar of data manipulation, as implemented in the R package **dplyr** [@R-dplyr], abstracts an coherent and consistent set of methods to handle a wide range of data transformation tasks. @r4ds argues that 80% of data analysis tasks can be solved with tidy tools while the remaining 20% requires other tools. [R]

@@

```{r write-bib}
write_bib(c("hts", "plm", "dplyr", "xts", "zoo"), file = "rpkgs.bib")
```

>>>>

@wickham2014tidy coined the term "tidy data", which is a rephrasing of the second and third normal forms in relational databases but in a way that makes more sense to data scientists. A suite of paired verbs such as `gather` and `spread` [@R-tidyr] were used to describe the reshape processing from messy data to tidy data. Tidy data, which standardized the mapping from the semantics of a dataset to its physical representation, serves remarkably as a fundamental unit of data analysis. R package **ggplot2** [@wickham2009ggplot2] pioneered developing the grammar of graphics based on tidy data, thus making it possible mapping from data space to visual elements. **dplyr** [@R-dplyr] generalised a coherent and consistent set of verbs to handle a wide range of data transformation tasks. @r4ds argues that 80% of data analysis tasks can be solved with tidy tools while the remaining 20% requires other tools. [R]

@@

```{r write-bib}
write_bib(c("dplyr", "tidyr"), file = "rpkgs.bib")
```
